---
title: "Analyses for the MS on Phylogenies of Interactions and Defaunation"
author: "Carine Emer y Miguel Verdú"
date: "13/06/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load packages}
library(picante)
library(phytools)
library(ape)
library(caper)
library(plyr)
library(reshape)
library(reshape2)
library(data.table)
library(dplyr)
library(bipartite)
library(Matrix)
library(lme4)
library(tibble)
library(phangorn)
library(plotly)
```


```{r input data}
setwd("~/Dropbox/Phylogenetic interactions/Phylogenies - Metanetwork Miguel/data and analyses")
load("~/Dropbox/Phylogenetic interactions/Phylogenies - Metanetwork Miguel/data/ms_phylogenies1.RData")

atlantic<-read.csv("working_data.csv", header=TRUE)
#data_pizo<-read.csv("frugivoria_Pizo natives.csv")
communities<-read.csv("data_communities nat.csv")
plants_taxon<-read.csv("plants_list_taxonomy_regional_pool.csv")

save.image("ms_phylogenies2.RData")

```

```{r filtering dataset}
#selecting interactions with birds only
data<-atlantic[atlantic$Frug_Class == "Aves",]

## selecting only native species, based on plants
data<-data[data$Plant_origin=="native",]
data<-droplevels(data) ## always check droplevels

##### remove interactions with Psittacideos, Corvideos and Columbidae which are mostly seed predators
data<-data[!data$Frug_Family==("Corvidae"),]
data<-data[!data$Frug_Family==("Psittacidae"),]
data<-data[!data$Frug_Family==("Columbidae"),]
data<-data[!data$Frugivore_Species2==("Estrilda_astrild"),] ## exotic
data<-droplevels(data)

### create a list of bird species that interact with native plant species, and are not seed predators, i.e., the list of bird species resulting from 'data' after removing alien spp, and some bird families, as above. We are working with the regional pool of species to estimate their ED
birds_list<-levels(data$Frugivore_Species2)
#birds_list_unique<-unique(birds_list[duplicated(birds_list)])## be very careful here because it is removing unique species that are not duplicated, as Fluvicola nengeta - notice later when merging with traits etc
#write.csv(birds_list,"birds_regional_pool1.csv") ## this list goes to birdtree.org to obtain 100 trees

####------------------------------------ Plants
### create a list of native plant species that interact with mutualistic birds, not seed predators, resulting from 'data' after removing alien spp, and some bird families, as above. 

#We are working with the regional pool of species to estimate their ED. 

#data<-data[!data$Plant_family==("Bromeliaceae"),] ## remove because of Aechmea nudicaulis not found in S. Phylomaker

levels(data$Plant_Species2)[levels(data$Plant_Species2)=="Zanthoxylum_fagara"] <- "Zanthoxylum_hyemale"
levels(data$Plant_Species2)[levels(data$Plant_Species2)=="Palicourea_forsteronioides"] <- "Psychotria_forsteronioides"
levels(data$Plant_Species2)[levels(data$Plant_Species2)=="Schinus_therebintifolia"] <- "Schinus_terebinthifolia"

levels(data$Plant_Species)[levels(data$Plant_Species)=="Zanthoxylum fagara"] <- "Zanthoxylum hyemale"
levels(data$Plant_Species)[levels(data$Plant_Species)=="Palicourea forsteronioides"] <- "Psychotria forsteronioides"
levels(data$Plant_Species)[levels(data$Plant_Species)=="Schinus therebentifolia"] <- "Schinus terebinthifolia"

data<-data[!data$Plant_Species2==("Duranta erecta"),] ### remove because it interacts with Estrilda - alien spp
data<-data[!data$Plant_Species==("Duranta erecta"),] ### remove because it interacts with Estrilda - alien spp

plants_list_atlantic<-levels(data$Plant_Species2)
plants_unique_atl<-as.data.frame(plants_list_atlantic)
names(plants_unique_atl)[names(plants_unique_atl) == 'plants_list_atlantic'] <- 'species'

write.csv(plants_unique_atl,"plants_list_regional_pool.csv")

#plants1<-merge(plants_unique_atl, plants_taxon,by="species", all.x= T, all.y=F) ## this merging is to get the genus and family columns to the list of species, only
#write.csv(plants1,"plants_list_taxonomy_regional_pool.csv") ##### fixed 'NA' in excel

```

```{r building tree plants, include= =FALSE}

########## PLANTS 
#phylo<-read.tree("PhytoPhylo.tre") # read in the megaphylogeny, obtained when downloading Phylomaker
#nodes<-read.csv("nodes.csv",header=T, sep="\t") # read in the nodes information of the megaphylogeny.
#source("S.PhyloMaker")
#plants_taxon<-read.csv("plants_list_taxonomy_regional_pool.csv")
#plants_taxon<-read.csv("plants_list_taxonomy.csv")
#result_plants<-S.PhyloMaker(splist=plants_taxon, tree=phylo, nodes=nodes) # run the function S.PhyloMaker.

#par(mfrow=c(1,3),mar=c(0,0,1,0)) # show the phylogenies of the three scenarios.
#plot(result_plants$Scenario.1,cex=1.1,main="Scenario One") ## we chose to work with scenario 1 that "assigns"add genera or species as basal polytomies within their families of genera" 
#plot(result$Scenario.2,cex=1.1,main="Scenario Two")
#plot(result$Scenario.3,cex=1.1,main="Scenario Three")
#is.binary.tree(result_plants$Scenario.1)

#write.nexus(result$Scenario.1,file="tree_phylomaker_1.nex") ### saving nexus format
#write.tree(result$Scenario.1,file="tree_phylomaker_1.nwk") ### saving newick format

#mytree<-result_plants$Scenario.1

########## using the saved newick format of the chosen scenario to plot the tree, or read the correspondent vector created above (mytree)
#tree_plants<-read.tree("tree_phylomaker_1.nwk")
#tree_plants<-mytree
#plot(tree_plants, cex=0.1) 
#zoom(tree_plants,240:280,show.node.label=TRUE)
#axisPhylo(tree_nplants)
#branching.times(tree_plants)

#library(ape)
#source("PolytomyResolver.R") #### function in the PolytomyResolver.R sent by Miguel Verdu

#tree_plants<-read.tree("tree_phylomaker_1.nwk") ### read the tree resolved in PhyloMaker, or use the vector created above

#PolytomyResolver(tree_plants,file="tree_plants") ### tree_plants.xml goes to BEAST - takes a few hours

### then, generates tree_plants.trees which should be read again here to run the following:

#trees<-read.nexus("tree_plants.trees") ## huge file


######### after BEAST

#postburnin<-trees[(0.25*length(trees)):length(trees)] #drops 25% of trees as burning 
 
#tt100<-sample(postburnin, size=100) #randomly selects 100 trees
#write.tree(tt100[[1]])
#plot(tt100,show.tip.label=FALSE)
#is.binary(tt100[[1]])

#tt100_1<-tt100[[1]]
#plot(tt100_1)
#write.tree(tt100,"plants_100trees.nwk")

```

```{r building tree birds, include==FALSE}

###### birds --- get bird.tre from birdtree.org
### in birdtree.org, source of trees = "Stage2 MayrParSho Hackett"

#bird_tree<-read.nexus("birds_tree.nex") # new format from birdtree


#bt100<-bird_tree #The list of trees here
#for (i in 1:length(bt100))
#{
#for (j in 1:length (sp)){
 #     bt100[[i]]<-add.species.to.genus(bt100[[i]], sp[j], 
  #                       where="random")}
#}

#write.tree(bt100,"birds_solved100_trees.nwk")

#setdiff(bt100[[1]]$tip.label,birds_list)
#setdiff(birds_list, bt100[[1]]$tip.label)

#write.tree(bt100[[1]]) ### the function uses the same object, so bt100
#plot(bt100[[1]])
#zoom(bt100[[1]],151:200, cex = 0.55)
#plot(b1, type="cladogram",cex = 0.35)
#plot(bird_tree, type="fan", cex = 0.95) ## chose type of output format of the tree
#axisPhylo() ## add branch lengths

#is.ultrametric(bt100[[100]])  ### to check whether the tips have the same total length since root
#diag(vcv(b1)) ## to check whether root to tip distance is the same for all tips
#range(diag(vcv(b1)))

```

calculating Evolutionary Distinctiveness
```{r ED birds, include= =FALSE}

bt100<-read.newick("birds_solved100_trees.nwk")

bt100<-lapply(bt100,drop.tip,tip="Estrilda_astrild") # exotic

#To calculate Evolutionary Distinctiveness across the 100 trees in the list

ED100<-lapply(bt100, evol.distinct)

#### to convert the list into a dataframe
for (i in 1: length(ED100)){ 
ED100[[i]]<-ED100[[i]][order(ED100[[i]]$Species),]}

ED100<-do.call(cbind.data.frame,ED100)
ED100<-ED100[,-seq (3, 200, 2),] ## exclude columns with species names but first one
rownames(ED100)<-ED100[,1] 
ED100<-ED100[,-1] ## exclude first column
colnames(ED100)<-paste("tree",1:100,sep="") ## give name to each column
ED100 <- cbind(Frugivore_Species2 = rownames(ED100), ED100) # give name to first column to later match with other df
rownames(ED100) <- NULL
write.csv(ED100,"birds_ED100.csv")
```

calculating ED plants
```{r ED plants, include= =FALSE}

tt100<-read.newick("plants_100trees.nwk")
tt100<-lapply(tt100,drop.tip,tip="Duranta_erecta")


#### evolutionary distinctiveness, function in Picante
ED100_p<-lapply(tt100, evol.distinct)

#### organize the list of EDs in a dataframe - columns
for (i in 1: length(ED100_p)){
ED100_p[[i]]<-ED100_p[[i]][order(ED100_p[[i]]$Species),]}
ED100_p<-do.call(cbind.data.frame,ED100_p)
ED100_p<-ED100_p[,-seq (3, 200, 2),] ## exclude columns with species names but first one
rownames(ED100_p)<-ED100_p[,1] 
ED100_p<-ED100_p[,-1] ## exclude first column
colnames(ED100_p)<-paste("tree",1:100,sep="") ## give name to each column
ED100_p <- cbind(Plant_Species2 = rownames(ED100_p), ED100_p) # give name to first column to later match with other df
rownames(ED100_p) <- NULL

write.csv(ED100_p,"plants_ED100.csv")
```

ED and traits (seed diameter and body mass) are correlated at the regional level in the Atlantic (ie, native species and interactions with mutualistic seed disperser birds) but ony body mass and ED are significanlty related at the communities level
```{r ED and traits species REGIONAL LEVEL}
###-------------------------- Body mass - 222 species at the regional level

## getting unique bird species and merging with their body mass (from Atlantic filtered as 'data', natives and mutualistic)
ED100<-read.csv("birds_ED100.csv", row.names = 1)

birds_unique<-as.data.frame(birds_list)
names(birds_unique)[names(birds_unique) == 'birds_list'] <- 'Frugivore_Species2'
#bm_birds<-merge(birds_unique, data,by="Frugivore_Species2", all.x= F, all.y=F)
bm_birds<-merge(birds_unique, data,by="Frugivore_Species2")
bm_birds<-bm_birds[,c("Frugivore_Species2", "Frug_Body_Mass", "Frugivore_Species", "interaction","Plant_Species2","seed_diameter", "Plant_Species")]
bm_unique_atl<-subset(bm_birds,!duplicated(bm_birds[,1]))
row.names(bm_unique_atl)<-bm_unique_atl$Frugivore_Species2
## checking that names of traits and tree are the same REGIONAL LEVEL
setdiff((bm_unique_atl$Frugivore_Species2),(ED100$Frugivore_Species2))
setdiff(ED100$Frugivore_Species2,bm_unique_atl$Frugivore_Species2)

removed<-setdiff(bm_unique_atl$Frugivore_Species2,bm_unique_commu2$Frugivore_Species2)

bm_unique_commu<-bm_unique_atl[-which(row.names(bm_unique_atl)%in%removed),]


ED100["mean_birds_ed"] <- rowMeans(ED100[,2:101])
bm_unique_atl["mean_birds_ed"] <- rowMeans(ED100[,2:101])
write.csv(ED100, "birds_ED100.csv")


###
### -------------------------Seed diameter - 440 species at the regional level

ED100_p<-read.csv("plants_ED100.csv", row.names = 1)

plants_unique<-as.data.frame(plants_list_atlantic)
names(plants_unique)[names(plants_unique) == 'plants_list_atlantic'] <- 'Plant_Species2'
sd_plants<-merge(plants_unique, data, by="Plant_Species2")
sd_plants<-sd_plants[,c("Frugivore_Species2", "Frug_Body_Mass", "Frugivore_Species", "interaction","Plant_Species2","seed_diameter", "Plant_Species")]
sd_unique_atl<-subset(sd_plants,!duplicated(sd_plants[,5]))

## checking that names of traits and tree are the same
setdiff((sd_unique_atl$Plant_Species2),(ED100_p$Plant_Species2))
setdiff(ED100_p$Plant_Species2,sd_unique_atl$Plant_Species2)

#quitar<-setdiff(row.names(ED100),(bm_unique$Frugivore_Species2))
#quitar<-setdiff((sd_unique_commu2$Plant_Species2),(ED100_p2$Plant_Species2))
#row.names(sd_unique)<-sd_unique$Plant_Species2
#sd_unique<-sd_unique[-which(row.names(sd_unique)%in%quitar),]

ED100_p["mean_plants_ed"] <- rowMeans(ED100_p[,2:101]) #### 
sd_unique_atl["mean_plants_ed"] <- rowMeans(ED100_p[,2:101]) ## 

write.csv(ED100_p, "plants_ED100.csv")
```

```{r filtering communities matrix, include = FALSE}
#Intervales
intervales<-subset(data, data$Study_Location_new == "PE Intervales")

intervales_new_unique<-subset(intervales, !duplicated(intervales[,"interaction"]))

intervales_new_unique<-intervales_new_unique[,c("Frugivore_Species", "Plant_Species")]
intervales_new_unique$abundance<-rep(1,nrow(intervales_new_unique))
intervales_new_unique<-intervales_new_unique[,c(2,3,1)]
intervales_new_unique<-droplevels(intervales_new_unique)
intervales_new_unique<-sample2matrix(intervales_new_unique)
intervales_matrix<-matrix2sample(intervales_new_unique)
dim(intervales_new_unique)

# Carlos Botelho
botelho<-subset(data, data$Study_Location_new == "PE Carlos Botelho")
botelho<-botelho[,c("Frugivore_Species", "Plant_Species", "interaction")]

botelho_new_unique<-subset(botelho, !duplicated(botelho[,"interaction"]))
botelho_new_unique<-botelho_new_unique[,c("Frugivore_Species", "Plant_Species")]
botelho_new_unique$abundance<-rep(1,nrow(botelho_new_unique))
botelho_new_unique<-botelho_new_unique[,c(2,3,1)]
botelho_new_unique<-droplevels(botelho_new_unique)
botelho_new_unique<-sample2matrix(botelho_new_unique)
nnzero(botelho_new_unique)

# Cardoso
cardoso<-subset(data, data$Study_Location_new == "PE Ilha do Cardoso")
cardoso<-cardoso[,c("Frugivore_Species", "Plant_Species", "interaction")]

cardoso_new_unique<-subset(cardoso, !duplicated(cardoso[,"interaction"]))
cardoso_new_unique<-cardoso_new_unique[,c("Frugivore_Species", "Plant_Species")]
cardoso_new_unique$abundance<-rep(1,nrow(cardoso_new_unique))
cardoso_new_unique<-cardoso_new_unique[,c(2,3,1)]
cardoso_new_unique<-droplevels(cardoso_new_unique)
cardoso_new_unique<-sample2matrix(cardoso_new_unique)
nnzero(cardoso_new_unique) ## count number of non zero cels - use to obtain number of interactions

stagenebra<-subset(data, data$Study_Location == "ARIE Santa Genebra"|data$Study.reference == "Figueiredo 1999")
stagenebra<-stagenebra[,c("Frugivore_Species", "Plant_Species")]
stagenebra$abundance<-rep(1,nrow(stagenebra))
stagenebra<-stagenebra[,c(2,3,1)]
stagenebra<-droplevels(stagenebra)
stagenebra<-sample2matrix(stagenebra)
nnzero(stagenebra)

######## communities that dont need merging
ufrj<-subset(data, data$Study_Location == "Campus UFRJ")
ufrj<-ufrj[,c("Frugivore_Species", "Plant_Species")]
ufrj$abundance<-rep(1,nrow(ufrj))
ufrj<-ufrj[,c(2,3,1)]
ufrj<-droplevels(ufrj)
ufrj<-sample2matrix(ufrj)

pira<-subset(data, data$Study.reference == "Robison V 2015")
pira<-pira[,c("Frugivore_Species", "Plant_Species")]
pira$abundance<-rep(1,nrow(pira))
pira<-pira[,c(2,3,1)]
pira<-droplevels(pira)
pira<-sample2matrix(pira)


fragmentSP<-subset(data, data$Study.reference == "Hasui 1994")
fragmentSP<-fragmentSP[,c("Frugivore_Species", "Plant_Species")]
fragmentSP$abundance<-rep(1,nrow(fragmentSP))
fragmentSP<-fragmentSP[,c(2,3,1)]
fragmentSP<-droplevels(fragmentSP)
fragmentSP<-sample2matrix(fragmentSP)

rebioAntas<-subset(data, data$Study_Location == "ReBio Poco Antas, RJ")
rebioAntas<-rebioAntas[,c("Frugivore_Species", "Plant_Species")]
rebioAntas$abundance<-rep(1,nrow(rebioAntas))
rebioAntas<-rebioAntas[,c(2,3,1)]
rebioAntas<-droplevels(rebioAntas)
rebioAntas<-sample2matrix(rebioAntas)

anchieta<-subset(data, data$Study_Location == "PE Ilha Anchieta, SP")
anchieta<-anchieta[,c("Frugivore_Species", "Plant_Species")]
anchieta$abundance<-rep(1,nrow(anchieta))
anchieta<-anchieta[,c(2,3,1)]
anchieta<-droplevels(anchieta)
anchieta<-sample2matrix(anchieta)

fragmentMG<-subset(data, data$Study.reference == "Fadini  R F 2004")
fragmentMG<-fragmentMG[,c("Frugivore_Species", "Plant_Species")]
fragmentMG$abundance<-rep(1,nrow(fragmentMG))
fragmentMG<-fragmentMG[,c(2,3,1)]
fragmentMG<-droplevels(fragmentMG)
fragmentMG<-sample2matrix(fragmentMG)

araucaria<-subset(data, data$Study.reference == "Kindel 1996")
araucaria<-araucaria[,c("Frugivore_Species", "Plant_Species")]
araucaria$abundance<-rep(1,nrow(araucaria))
araucaria<-araucaria[,c(2,3,1)]
araucaria<-droplevels(araucaria)
araucaria<-sample2matrix(araucaria)

itatiba<-subset(data, data$Study_Location == "Itatiba, SP")
itatiba<-itatiba[,c("Frugivore_Species", "Plant_Species")]
itatiba$abundance<-rep(1,nrow(itatiba))
itatiba<-itatiba[,c(2,3,1)]
itatiba<-droplevels(itatiba)
itatiba<-sample2matrix(itatiba)

fragmentRC<-subset(data, data$Study_Location == "Usina Parque do Corumbatai, Rio Claro - SP")
fragmentRC<-fragmentRC[,c("Frugivore_Species", "Plant_Species")]
fragmentRC$abundance<-rep(1,nrow(fragmentRC))
fragmentRC<-fragmentRC[,c(2,3,1)]
fragmentRC<-droplevels(fragmentRC)
fragmentRC<-sample2matrix(fragmentRC)

restored57<-subset(data, data$Study.reference == "Ribeiro  F (unpublish) 57")
restored57<-restored57[,c("Frugivore_Species", "Plant_Species")]
restored57$abundance<-rep(1,nrow(restored57))
restored57<-restored57[,c(2,3,1)]
restored57<-droplevels(restored57)
restored57<-sample2matrix(restored57)

restored25<-subset(data, data$Study.reference == "Ribeiro  F (unpublish) 25")
restored25<-restored25[,c("Frugivore_Species", "Plant_Species")]
restored25$abundance<-rep(1,nrow(restored25))
restored25<-restored25[,c(2,3,1)]
restored25<-droplevels(restored25)
restored25<-sample2matrix(restored25)

restored15<-subset(data, data$Study.reference == "Ribeiro  F (unpublish) 15")
restored15<-restored15[,c("Frugivore_Species", "Plant_Species")]
restored15$abundance<-rep(1,nrow(restored15))
restored15<-restored15[,c(2,3,1)]
restored15<-droplevels(restored15)
restored15<-sample2matrix(restored15)

###### communities added from Pizo - Atlantic

comboios<-subset(data, data$Study.reference == "Argel de Oliveira  1999 ")  # note the space after 1999 in the Atlantic 
comboios<-comboios[,c("Frugivore_Species", "Plant_Species")]
comboios$abundance<-rep(1,nrow(comboios))
comboios<-comboios[,c(2,3,1)]
comboios<-droplevels(comboios)
comboios<-sample2matrix(comboios)

itapua<-subset(data, data$Study.reference == "Scherer et al 2007") ### restinga?
itapua<-itapua[,c("Frugivore_Species", "Plant_Species")]
itapua$abundance<-rep(1,nrow(itapua))
itapua<-itapua[,c(2,3,1)]
itapua<-droplevels(itapua)
itapua<-sample2matrix(itapua)

reservasRJ<-subset(data, data$Study_Location == "PARNA Serra Orgaos"|data$Study_Location == "PE Tres Picos, RJ")
reservasRJ<-reservasRJ[,c("Frugivore_Species", "Plant_Species")]
reservasRJ$abundance<-rep(1,nrow(reservasRJ))
reservasRJ<-reservasRJ[,c(2,3,1)]
reservasRJ<-droplevels(reservasRJ)
reservasRJ<-sample2matrix(reservasRJ)

ibitipoca<-subset(data, data$Study.reference == "Manhaes 2003") 
ibitipoca<-ibitipoca[,c("Frugivore_Species", "Plant_Species")]
ibitipoca$abundance<-rep(1,nrow(ibitipoca))
ibitipoca<-ibitipoca[,c(2,3,1)]
ibitipoca<-droplevels(ibitipoca)
ibitipoca<-sample2matrix(ibitipoca)

jurubatiba<-subset(data, data$Study_Location == "Jurubatiba") ### community added to Atlantic by Pizo/Erisson
jurubatiba<-jurubatiba[,c("Frugivore_Species", "Plant_Species")]
jurubatiba$abundance<-rep(1,nrow(jurubatiba))
jurubatiba<-jurubatiba[,c(2,3,1)]
jurubatiba<-droplevels(jurubatiba)
jurubatiba<-sample2matrix(jurubatiba)
nnzero(jurubatiba)
dim(jurubatiba)
```

```{r filtering communities body mass, include = FALSE}
#bm_unique_atl$Frugivore_Species<-gsub("_"," ",bm_unique$Frugivore_Species)

itapua1<-matrix2sample(itapua)
birds_itapua<-itapua1$id
b_itapua<-droplevels(birds_itapua)
b_itapua<-as.data.frame(b_itapua)
b_itapua<-subset(b_itapua,!duplicated(b_itapua))
names(b_itapua)[1]<-paste("Frugivore_Species")
b_itapua_bm<-merge(b_itapua,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
#b_itapua_bm1<-join(b_itapua,bm_unique,by="Frugivore_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
str(b_itapua_bm)

b_itapua_bm[,9]<-NULL
b_itapua_bm$site<-with(b_itapua_bm,"itapua")
mean_bm_itapua<-mean(b_itapua_bm[,"Frug_Body_Mass"],na.rm=TRUE)

intervales1<-matrix2sample(intervales_new_unique)
birds_intervales<-intervales1$id
b_intervales<-droplevels(birds_intervales)
b_intervales<-as.data.frame(b_intervales)
b_intervales<-subset(b_intervales,!duplicated(b_intervales))
names(b_intervales)[1]<-paste("Frugivore_Species")
b_intervales_bm<-merge(b_intervales,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
dim(b_intervales_bm)
b_intervales_bm[,9]<-NULL
b_intervales_bm$site<-with(b_intervales_bm,"intervales")
mean_bm_intervales<-mean(b_intervales_bm[,"Frug_Body_Mass"],na.rm=TRUE)

cardoso1<-matrix2sample(cardoso_new_unique)
birds_cardoso<-cardoso1$id
b_cardoso<-droplevels(birds_cardoso)
b_cardoso<-as.data.frame(b_cardoso)
b_cardoso<-subset(b_cardoso,!duplicated(b_cardoso))
names(b_cardoso)[1]<-paste("Frugivore_Species")
b_cardoso_bm<-merge(b_cardoso,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
dim(b_cardoso_bm)
b_cardoso_bm[,9]<-NULL
b_cardoso_bm$site<-with(b_cardoso_bm,"cardoso")
mean_bm_cardoso<-mean(b_cardoso_bm[,"Frug_Body_Mass"],na.rm=TRUE)

botelho1<-matrix2sample(botelho_new_unique)
birds_botelho<-botelho1$id
b_botelho<-droplevels(birds_botelho)
b_botelho<-as.data.frame(b_botelho)
b_botelho<-subset(b_botelho,!duplicated(b_botelho))
names(b_botelho)[1]<-paste("Frugivore_Species")
b_botelho_bm<-merge(b_botelho,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_botelho_bm[,9]<-NULL
b_botelho_bm$site<-with(b_botelho_bm,"botelho")
mean_bm_botelho<-mean(b_botelho_bm[,"Frug_Body_Mass"],na.rm=TRUE)

rebioAntas1<-matrix2sample(rebioAntas)
birds_rebioAntas<-rebioAntas1$id
b_rebioAntas<-droplevels(birds_rebioAntas)
b_rebioAntas<-as.data.frame(b_rebioAntas)
b_rebioAntas<-subset(b_rebioAntas,!duplicated(b_rebioAntas))
names(b_rebioAntas)[1]<-paste("Frugivore_Species")
b_rebioAntas_bm<-merge(b_rebioAntas,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_rebioAntas_bm[,9]<-NULL
b_rebioAntas_bm$site<-with(b_rebioAntas_bm,"rebioAntas")
mean_bm_rebioAntas<-mean(b_rebioAntas_bm[,"Frug_Body_Mass"],na.rm=TRUE)

stagenebra1<-matrix2sample(stagenebra)
birds_stagenebra<-stagenebra1$id
b_stagenebra<-droplevels(birds_stagenebra)
b_stagenebra<-as.data.frame(b_stagenebra)
b_stagenebra<-subset(b_stagenebra,!duplicated(b_stagenebra))
names(b_stagenebra)[1]<-paste("Frugivore_Species")
b_stagenebra_bm<-merge(b_stagenebra,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_stagenebra_bm[,9]<-NULL
b_stagenebra_bm$site<-with(b_stagenebra_bm,"stagenebra")
mean_bm_stagenebra<-mean(b_stagenebra_bm[,"Frug_Body_Mass"],na.rm=TRUE)


anchieta1<-matrix2sample(anchieta)
birds_anchieta<-anchieta1$id
b_anchieta<-droplevels(birds_anchieta)
b_anchieta<-as.data.frame(b_anchieta)
b_anchieta<-subset(b_anchieta,!duplicated(b_anchieta))
names(b_anchieta)[1]<-paste("Frugivore_Species")
b_anchieta_bm<-merge(b_anchieta,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_anchieta_bm[,9]<-NULL
b_anchieta_bm$site<-with(b_anchieta_bm,"anchieta")
mean_bm_anchieta<-mean(b_anchieta_bm[,"Frug_Body_Mass"],na.rm=TRUE)


fragmentMG1<-matrix2sample(fragmentMG)
birds_fragmentMG<-fragmentMG1$id
b_fragmentMG<-droplevels(birds_fragmentMG)
b_fragmentMG<-as.data.frame(b_fragmentMG)
b_fragmentMG<-subset(b_fragmentMG,!duplicated(b_fragmentMG))
names(b_fragmentMG)[1]<-paste("Frugivore_Species")
b_fragmentMG_bm<-merge(b_fragmentMG,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_fragmentMG_bm[,9]<-NULL
b_fragmentMG_bm$site<-with(b_fragmentMG_bm,"fragmentMG")
mean_bm_fragmentMG<-mean(b_fragmentMG_bm[,"Frug_Body_Mass"],na.rm=TRUE)

araucaria1<-matrix2sample(araucaria)
birds_araucaria<-araucaria1$id
b_araucaria<-droplevels(birds_araucaria)
b_araucaria<-as.data.frame(b_araucaria)
b_araucaria<-subset(b_araucaria,!duplicated(b_araucaria))
names(b_araucaria)[1]<-paste("Frugivore_Species")
b_araucaria_bm<-merge(b_araucaria,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_araucaria_bm[,9]<-NULL
b_araucaria_bm$site<-with(b_araucaria_bm,"araucaria")
mean_bm_araucaria<-mean(b_araucaria_bm[,"Frug_Body_Mass"],na.rm=TRUE)

itatiba1<-matrix2sample(itatiba)
birds_itatiba<-itatiba1$id
b_itatiba<-droplevels(birds_itatiba)
b_itatiba<-as.data.frame(b_itatiba)
b_itatiba<-subset(b_itatiba,!duplicated(b_itatiba))
names(b_itatiba)[1]<-paste("Frugivore_Species")
b_itatiba_bm<-merge(b_itatiba,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_itatiba_bm[,9]<-NULL
b_itatiba_bm$site<-with(b_itatiba_bm,"itatiba")
mean_bm_itatiba<-mean(b_itatiba_bm[,"Frug_Body_Mass"],na.rm=TRUE)

fragmentRC1<-matrix2sample(fragmentRC)
birds_fragmentRC<-fragmentRC1$id
b_fragmentRC<-droplevels(birds_fragmentRC)
b_fragmentRC<-as.data.frame(b_fragmentRC)
b_fragmentRC<-subset(b_fragmentRC,!duplicated(b_fragmentRC))
names(b_fragmentRC)[1]<-paste("Frugivore_Species")
b_fragmentRC_bm<-merge(b_fragmentRC,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_fragmentRC_bm[,9]<-NULL
b_fragmentRC_bm$site<-with(b_fragmentRC_bm,"fragmentRC")
mean_bm_fragmentRC<-mean(b_fragmentRC_bm[,"Frug_Body_Mass"],na.rm=TRUE)

restored571<-matrix2sample(restored57)
birds_restored57<-restored571$id
b_restored57<-droplevels(birds_restored57)
b_restored57<-as.data.frame(b_restored57)
b_restored57<-subset(b_restored57,!duplicated(b_restored57))
names(b_restored57)[1]<-paste("Frugivore_Species")
b_restored57_bm<-merge(b_restored57,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_restored57_bm[,9]<-NULL
b_restored57_bm$site<-with(b_restored57_bm,"restored57")
mean_bm_restored57<-mean(b_restored57_bm[,"Frug_Body_Mass"],na.rm=TRUE)

restored251<-matrix2sample(restored25)
birds_restored25<-restored251$id
b_restored25<-droplevels(birds_restored25)
b_restored25<-as.data.frame(b_restored25)
b_restored25<-subset(b_restored25,!duplicated(b_restored25))
names(b_restored25)[1]<-paste("Frugivore_Species")
b_restored25_bm<-merge(b_restored25,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_restored25_bm[,9]<-NULL
b_restored25_bm$site<-with(b_restored25_bm,"restored25")
mean_bm_restored25<-mean(b_restored25_bm[,"Frug_Body_Mass"],na.rm=TRUE)

restored151<-matrix2sample(restored15)
birds_restored15<-restored151$id
b_restored15<-droplevels(birds_restored15)
b_restored15<-as.data.frame(b_restored15)
b_restored15<-subset(b_restored15,!duplicated(b_restored15))
names(b_restored15)[1]<-paste("Frugivore_Species")
b_restored15_bm<-merge(b_restored15,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_restored15_bm[,9]<-NULL
b_restored15_bm$site<-with(b_restored15_bm,"restored15")
mean_bm_restored15<-mean(b_restored15_bm[,"Frug_Body_Mass"],na.rm=TRUE)

fragmentSP1<-matrix2sample(fragmentSP)
birds_fragmentSP<-fragmentSP1$id
b_fragmentSP<-droplevels(birds_fragmentSP)
b_fragmentSP<-as.data.frame(b_fragmentSP)
b_fragmentSP<-subset(b_fragmentSP,!duplicated(b_fragmentSP))
names(b_fragmentSP)[1]<-paste("Frugivore_Species")
b_fragmentSP_bm<-merge(b_fragmentSP,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_fragmentSP_bm[,9]<-NULL
b_fragmentSP_bm$site<-with(b_fragmentSP_bm,"fragmentSP")
mean_bm_fragmentSP<-mean(b_fragmentSP_bm[,"Frug_Body_Mass"],na.rm=TRUE)

pira1<-matrix2sample(pira)
birds_pira<-pira1$id
b_pira<-droplevels(birds_pira)
b_pira<-as.data.frame(b_pira)
b_pira<-subset(b_pira,!duplicated(b_pira))
names(b_pira)[1]<-paste("Frugivore_Species")
b_pira_bm<-merge(b_pira,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_pira_bm[,9]<-NULL
b_pira_bm$site<-with(b_pira_bm,"pira")
mean_bm_pira<-mean(b_pira_bm[,"Frug_Body_Mass"],na.rm=TRUE)

ufrj1<-matrix2sample(ufrj)
birds_ufrj<-ufrj1$id
b_ufrj<-droplevels(birds_ufrj)
b_ufrj<-as.data.frame(b_ufrj)
b_ufrj<-subset(b_ufrj,!duplicated(b_ufrj))
names(b_ufrj)[1]<-paste("Frugivore_Species")
b_ufrj_bm<-merge(b_ufrj,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_ufrj_bm[,9]<-NULL
b_ufrj_bm$site<-with(b_ufrj_bm,"ufrj")
mean_bm_ufrj<-mean(b_ufrj_bm[,"Frug_Body_Mass"],na.rm=TRUE)

comboios1<-matrix2sample(comboios)
birds_comboios<-comboios1$id
b_comboios<-droplevels(birds_comboios)
b_comboios<-as.data.frame(b_comboios)
b_comboios<-subset(b_comboios,!duplicated(b_comboios))
names(b_comboios)[1]<-paste("Frugivore_Species")
b_comboios_bm<-merge(b_comboios,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_comboios_bm[,9]<-NULL
b_comboios_bm$site<-with(b_comboios_bm,"comboios")
mean_bm_comboios<-mean(b_comboios_bm[,"Frug_Body_Mass"],na.rm=TRUE)

reservasRJ1<-matrix2sample(reservasRJ)
birds_reservasRJ<-reservasRJ1$id
b_reservasRJ<-droplevels(birds_reservasRJ)
b_reservasRJ<-as.data.frame(b_reservasRJ)
b_reservasRJ<-subset(b_reservasRJ,!duplicated(b_reservasRJ))
names(b_reservasRJ)[1]<-paste("Frugivore_Species")
b_reservasRJ_bm<-merge(b_reservasRJ,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_reservasRJ_bm[,9]<-NULL
b_reservasRJ_bm$site<-with(b_reservasRJ_bm,"reservasRJ")
mean_bm_reservasRJ<-mean(b_reservasRJ_bm[,"Frug_Body_Mass"],na.rm=TRUE)

ibitipoca1<-matrix2sample(ibitipoca)
birds_ibitipoca<-ibitipoca1$id
b_ibitipoca<-droplevels(birds_ibitipoca)
b_ibitipoca<-as.data.frame(b_ibitipoca)
b_ibitipoca<-subset(b_ibitipoca,!duplicated(b_ibitipoca))
names(b_ibitipoca)[1]<-paste("Frugivore_Species")
b_ibitipoca_bm<-merge(b_ibitipoca,bm_unique_atl,by="Frugivore_Species",all.x = F,all.y = F)
b_ibitipoca_bm[,9]<-NULL
b_ibitipoca_bm$site<-with(b_ibitipoca_bm,"ibitipoca")
mean_bm_ibitipoca<-mean(b_ibitipoca_bm[,"Frug_Body_Mass"],na.rm=TRUE)

jurubatiba1<-matrix2sample(jurubatiba)
birds_jurubatiba<-jurubatiba1$id
b_jurubatiba<-droplevels(birds_jurubatiba)
b_jurubatiba<-as.data.frame(b_jurubatiba)
b_jurubatiba<-subset(b_jurubatiba,!duplicated(b_jurubatiba))
names(b_jurubatiba)[1]<-paste("Frugivore_Species")
b_jurubatiba_bm<-merge(b_jurubatiba,bm_unique_atl,by="Frugivore_Species",all.x = T,all.y = F)
dim(b_jurubatiba_bm)
b_jurubatiba_bm[,9]<-NULL
b_jurubatiba_bm$site<-with(b_jurubatiba_bm,"jurubatiba")
mean_bm_jurubatiba<-mean(b_jurubatiba_bm[,"Frug_Body_Mass"],na.rm=TRUE)

##### merging all communities with their bodymass
### 
commu_bm_list<-list(b_intervales_bm, b_cardoso_bm, b_botelho_bm,
                      b_rebioAntas_bm, b_anchieta_bm,b_araucaria_bm,
                      b_fragmentMG_bm, b_fragmentRC_bm,b_fragmentSP_bm,                      b_stagenebra_bm, b_itatiba_bm, b_itapua_bm,                      b_restored57_bm, b_restored25_bm, b_restored15_bm,                      b_pira_bm, b_jurubatiba_bm, b_ibitipoca_bm,                      b_ufrj_bm, b_reservasRJ_bm, b_comboios_bm)

bm_commu<-merge_all(commu_bm_list) # function from reshape
```

```{r filtering communities seed diameter, include = FALSE}

itapua1<-matrix2sample(itapua)
plants_itapua<-itapua1$plot
p_itapua<-droplevels(plants_itapua)
p_itapua<-as.data.frame(p_itapua)
p_itapua<-subset(p_itapua,!duplicated(p_itapua))
names(p_itapua)[1]<-paste("Plant_Species")
p_itapua_sd<-merge(p_itapua,sd_unique_atl,by="Plant_Species",all.x = F,all.y = F)
#b_itapua_bm1<-join(b_itapua,bm_unique_atl,by="Frugivore_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_itapua_sd)
p_itapua_sd[,8]<-NULL
p_itapua_sd$site<-with(p_itapua_sd,"itapua")

intervales1<-matrix2sample(intervales_new_unique)
plants_intervales<-intervales1$plot
p_intervales<-droplevels(plants_intervales)
p_intervales<-as.data.frame(p_intervales)
p_intervales<-subset(p_intervales,!duplicated(p_intervales))
names(p_intervales)[1]<-paste("Plant_Species")
p_intervales_sd<-join(p_intervales,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_intervales_sd)
p_intervales_sd[,8]<-NULL
p_intervales_sd$site<-with(p_intervales_sd,"intervales")

cardoso2<-matrix2sample(cardoso_new_unique)
plants_cardoso<-cardoso2$plot
p_cardoso<-droplevels(plants_cardoso)
p_cardoso<-as.data.frame(p_cardoso)
p_cardoso<-subset(p_cardoso,!duplicated(p_cardoso))
names(p_cardoso)[1]<-paste("Plant_Species")
p_cardoso_sd<-join(p_cardoso,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_cardoso_sd)
p_cardoso_sd[,8]<-NULL
p_cardoso_sd$site<-with(p_cardoso_sd,"cardoso")

botelho2<-matrix2sample(botelho_new_unique)
plants_botelho<-botelho2$plot
p_botelho<-droplevels(plants_botelho)
p_botelho<-as.data.frame(p_botelho)
p_botelho<-subset(p_botelho,!duplicated(p_botelho))
names(p_botelho)[1]<-paste("Plant_Species")
p_botelho_sd<-join(p_botelho,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_botelho_sd)
p_botelho_sd[,8]<-NULL
p_botelho_sd$site<-with(p_botelho_sd,"botelho")

rebioAntas2<-matrix2sample(rebioAntas)
plants_rebioAntas<-rebioAntas2$plot
p_rebioAntas<-droplevels(plants_rebioAntas)
p_rebioAntas<-as.data.frame(p_rebioAntas)
p_rebioAntas<-subset(p_rebioAntas,!duplicated(p_rebioAntas))
names(p_rebioAntas)[1]<-paste("Plant_Species")
p_rebioAntas_sd<-join(p_rebioAntas,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_rebioAntas_sd)
p_rebioAntas_sd[,8]<-NULL
p_rebioAntas_sd$site<-with(p_rebioAntas_sd,"rebioAntas")

stagenebra2<-matrix2sample(stagenebra)
plants_stagenebra<-stagenebra2$plot
p_stagenebra<-droplevels(plants_stagenebra)
p_stagenebra<-as.data.frame(p_stagenebra)
p_stagenebra<-subset(p_stagenebra,!duplicated(p_stagenebra))
names(p_stagenebra)[1]<-paste("Plant_Species")
p_stagenebra_sd<-join(p_stagenebra,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_stagenebra_sd)
p_stagenebra_sd[,8]<-NULL
p_stagenebra_sd$site<-with(p_stagenebra_sd,"stagenebra")

rebioAntas2<-matrix2sample(rebioAntas)
plants_rebioAntas<-rebioAntas2$plot
p_rebioAntas<-droplevels(plants_rebioAntas)
p_rebioAntas<-as.data.frame(p_rebioAntas)
p_rebioAntas<-subset(p_rebioAntas,!duplicated(p_rebioAntas))
names(p_rebioAntas)[1]<-paste("Plant_Species")
p_rebioAntas_sd<-join(p_rebioAntas,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_rebioAntas_sd)
p_rebioAntas_sd[,8]<-NULL
p_rebioAntas_sd$site<-with(p_rebioAntas_sd,"rebioAntas")

anchieta2<-matrix2sample(anchieta)
plants_anchieta<-anchieta2$plot
p_anchieta<-droplevels(plants_anchieta)
p_anchieta<-as.data.frame(p_anchieta)
p_anchieta<-subset(p_anchieta,!duplicated(p_anchieta))
names(p_anchieta)[1]<-paste("Plant_Species")
p_anchieta_sd<-join(p_anchieta,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_anchieta_sd)
p_anchieta_sd[,8]<-NULL
p_anchieta_sd$site<-with(p_anchieta_sd,"anchieta")

fragmentMG2<-matrix2sample(fragmentMG)
plants_fragmentMG<-fragmentMG2$plot
p_fragmentMG<-droplevels(plants_fragmentMG)
p_fragmentMG<-as.data.frame(p_fragmentMG)
p_fragmentMG<-subset(p_fragmentMG,!duplicated(p_fragmentMG))
names(p_fragmentMG)[1]<-paste("Plant_Species")
p_fragmentMG_sd<-join(p_fragmentMG,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_fragmentMG_sd)
p_fragmentMG_sd[,8]<-NULL
p_fragmentMG_sd$site<-with(p_fragmentMG_sd,"fragmentMG")

araucaria2<-matrix2sample(araucaria)
plants_araucaria<-araucaria2$plot
p_araucaria<-droplevels(plants_araucaria)
p_araucaria<-as.data.frame(p_araucaria)
p_araucaria<-subset(p_araucaria,!duplicated(p_araucaria))
names(p_araucaria)[1]<-paste("Plant_Species")
p_araucaria_sd<-join(p_araucaria,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_araucaria_sd)
p_araucaria_sd[,8]<-NULL
p_araucaria_sd$site<-with(p_araucaria_sd,"araucaria")

itatiba2<-matrix2sample(itatiba)
plants_itatiba<-itatiba2$plot
p_itatiba<-droplevels(plants_itatiba)
p_itatiba<-as.data.frame(p_itatiba)
p_itatiba<-subset(p_itatiba,!duplicated(p_itatiba))
names(p_itatiba)[1]<-paste("Plant_Species")
p_itatiba_sd<-join(p_itatiba,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_itatiba_sd)
p_itatiba_sd[,8]<-NULL
p_itatiba_sd$site<-with(p_itatiba_sd,"itatiba")

fragmentRC2<-matrix2sample(fragmentRC)
plants_fragmentRC<-fragmentRC2$plot
p_fragmentRC<-droplevels(plants_fragmentRC)
p_fragmentRC<-as.data.frame(p_fragmentRC)
p_fragmentRC<-subset(p_fragmentRC,!duplicated(p_fragmentRC))
names(p_fragmentRC)[1]<-paste("Plant_Species")
p_fragmentRC_sd<-join(p_fragmentRC,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_fragmentRC_sd)
p_fragmentRC_sd[,8]<-NULL
p_fragmentRC_sd$site<-with(p_fragmentRC_sd,"fragmentRC")

restored572<-matrix2sample(restored57)
plants_restored57<-restored572$plot
p_restored57<-droplevels(plants_restored57)
p_restored57<-as.data.frame(p_restored57)
p_restored57<-subset(p_restored57,!duplicated(p_restored57))
names(p_restored57)[1]<-paste("Plant_Species")
p_restored57_sd<-join(p_restored57,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_restored57_sd)
p_restored57_sd[,8]<-NULL
p_restored57_sd$site<-with(p_restored57_sd,"restored57")

restored252<-matrix2sample(restored25)
plants_restored25<-restored252$plot
p_restored25<-droplevels(plants_restored25)
p_restored25<-as.data.frame(p_restored25)
p_restored25<-subset(p_restored25,!duplicated(p_restored25))
names(p_restored25)[1]<-paste("Plant_Species")
p_restored25_sd<-join(p_restored25,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_restored25_sd)
p_restored25_sd[,8]<-NULL
p_restored25_sd$site<-with(p_restored25_sd,"restored25")

restored152<-matrix2sample(restored15)
plants_restored15<-restored152$plot
p_restored15<-droplevels(plants_restored15)
p_restored15<-as.data.frame(p_restored15)
p_restored15<-subset(p_restored15,!duplicated(p_restored15))
names(p_restored15)[1]<-paste("Plant_Species")
p_restored15_sd<-join(p_restored15,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_restored15_sd)
p_restored15_sd[,8]<-NULL
p_restored15_sd$site<-with(p_restored15_sd,"restored15")

fragmentSP2<-matrix2sample(fragmentSP)
plants_fragmentSP<-fragmentSP2$plot
p_fragmentSP<-droplevels(plants_fragmentSP)
p_fragmentSP<-as.data.frame(p_fragmentSP)
p_fragmentSP<-subset(p_fragmentSP,!duplicated(p_fragmentSP))
names(p_fragmentSP)[1]<-paste("Plant_Species")
p_fragmentSP_sd<-join(p_fragmentSP,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_fragmentSP_sd)
p_fragmentSP_sd[,8]<-NULL
p_fragmentSP_sd$site<-with(p_fragmentSP_sd,"fragmentSP")

pira2<-matrix2sample(pira)
plants_pira<-pira2$plot
p_pira<-droplevels(plants_pira)
p_pira<-as.data.frame(p_pira)
p_pira<-subset(p_pira,!duplicated(p_pira))
names(p_pira)[1]<-paste("Plant_Species")
p_pira_sd<-join(p_pira,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_pira_sd)
p_pira_sd[,8]<-NULL
p_pira_sd$site<-with(p_pira_sd,"pira")

ufrj2<-matrix2sample(ufrj)
plants_ufrj<-ufrj2$plot
p_ufrj<-droplevels(plants_ufrj)
p_ufrj<-as.data.frame(p_ufrj)
p_ufrj<-subset(p_ufrj,!duplicated(p_ufrj))
names(p_ufrj)[1]<-paste("Plant_Species")
p_ufrj_sd<-join(p_ufrj,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_ufrj_sd)
p_ufrj_sd[,8]<-NULL
p_ufrj_sd$site<-with(p_ufrj_sd,"ufrj")

comboios2<-matrix2sample(comboios)
plants_comboios<-comboios2$plot
p_comboios<-droplevels(plants_comboios)
p_comboios<-as.data.frame(p_comboios)
p_comboios<-subset(p_comboios,!duplicated(p_comboios))
names(p_comboios)[1]<-paste("Plant_Species")
p_comboios_sd<-join(p_comboios,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_comboios_sd)
p_comboios_sd[,8]<-NULL
p_comboios_sd$site<-with(p_comboios_sd,"comboios")

reservasRJ2<-matrix2sample(reservasRJ)
plants_reservasRJ<-reservasRJ2$plot
p_reservasRJ<-droplevels(plants_reservasRJ)
p_reservasRJ<-as.data.frame(p_reservasRJ)
p_reservasRJ<-subset(p_reservasRJ,!duplicated(p_reservasRJ))
names(p_reservasRJ)[1]<-paste("Plant_Species")
p_reservasRJ_sd<-join(p_reservasRJ,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_reservasRJ_sd)
p_reservasRJ_sd[,8]<-NULL
p_reservasRJ_sd$site<-with(p_reservasRJ_sd,"reservasRJ")

ibitipoca2<-matrix2sample(ibitipoca)
plants_ibitipoca<-ibitipoca2$plot
p_ibitipoca<-droplevels(plants_ibitipoca)
p_ibitipoca<-as.data.frame(p_ibitipoca)
p_ibitipoca<-subset(p_ibitipoca,!duplicated(p_ibitipoca))
names(p_ibitipoca)[1]<-paste("Plant_Species")
p_ibitipoca_sd<-join(p_ibitipoca,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_ibitipoca_sd)
p_ibitipoca_sd[,8]<-NULL
p_ibitipoca_sd$site<-with(p_ibitipoca_sd,"ibitipoca")

jurubatiba2<-matrix2sample(jurubatiba)
plants_jurubatiba<-jurubatiba2$plot
p_jurubatiba<-droplevels(plants_jurubatiba)
p_jurubatiba<-as.data.frame(p_jurubatiba)
p_jurubatiba<-subset(p_jurubatiba,!duplicated(p_jurubatiba))
names(p_jurubatiba)[1]<-paste("Plant_Species")
p_jurubatiba_sd<-join(p_jurubatiba,sd_unique_atl,by="Plant_Species", type = "left") # an option for merge - if it doesnt work, but it is given same results here
dim(p_jurubatiba_sd)
p_jurubatiba_sd[,8]<-NULL
p_jurubatiba_sd$site<-with(p_jurubatiba_sd,"jurubatiba")


##### merging all communities with their bodymass
### 
commu_sd_list<-list(p_intervales_sd, p_cardoso_sd, p_botelho_sd,
                      p_rebioAntas_sd, p_anchieta_sd, p_araucaria_sd,
                      p_fragmentMG_sd, p_fragmentRC_sd, p_fragmentSP_sd,
                      p_stagenebra_sd, p_itatiba_sd, p_itapua_sd,
                      p_restored57_sd, p_restored25_sd, p_restored15_sd,
                      p_pira_sd, p_jurubatiba_sd, p_ibitipoca_sd,
                      p_ufrj_sd, p_reservasRJ_sd, p_comboios_sd)


sd_commu<-merge_all(commu_sd_list) # function from reshape
str(sd_commu)
setdiff(sd_commu$Plant_Species2, ED100_p$Plant_Species2)
setdiff(ED100_p$Plant_Species2, sd_commu$Plant_Species2)
```

```{r filtering communities int, include = FALSE}

### obtain a list of interactions per site
intervales<-subset(data, data$Study_Location_new == "PE Intervales")
intervales_i<-intervales[,c("Frugivore_Species", "Plant_Species", "interaction")]
intervales_i<-subset(intervales_i,!duplicated(intervales_i[,3]))
intervales_i[,4]<-NULL
intervales_i$site<-with(intervales_i,"intervales")


stagenebra<-subset(data, data$Study_Location == "ARIE Santa Genebra"|data$Study.reference == "Figueiredo 1999")
stagenebra_i<-stagenebra[,c("Frugivore_Species", "Plant_Species","interaction")]
stagenebra_i<-subset(stagenebra_i,!duplicated(stagenebra_i[,3]))
stagenebra_i[,4]<-NULL
stagenebra_i$site<-with(stagenebra_i,"stagenebra")


ufrj<-subset(data, data$Study_Location == "Campus UFRJ")
ufrj_i<-ufrj[,c("Frugivore_Species", "Plant_Species", "interaction")]
ufrj_i[,4]<-NULL
ufrj_i$site<-with(ufrj_i,"ufrj")

pira<-subset(data, data$Study.reference == "Robison V 2015")
pira_i<-pira[,c("Frugivore_Species", "Plant_Species", "interaction")]
pira_i[,4]<-NULL
pira_i$site<-with(pira_i,"pira")

fragmentSP<-subset(data, data$Study.reference == "Hasui 1994")
fragmentSP_i<-fragmentSP[,c("Frugivore_Species", "Plant_Species", "interaction")]
fragmentSP_i[,4]<-NULL
fragmentSP_i$site<-with(fragmentSP_i,"fragmentSP")

rebioAntas<-subset(data, data$Study_Location == "ReBio Poco Antas, RJ")
rebioAntas_i<-rebioAntas[,c("Frugivore_Species", "Plant_Species","interaction")]
rebioAntas_i[,4]<-NULL
rebioAntas_i$site<-with(rebioAntas_i,"rebioAntas")

anchieta<-subset(data, data$Study_Location == "PE Ilha Anchieta, SP")
anchieta_i<-anchieta[,c("Frugivore_Species", "Plant_Species","interaction")]
anchieta_i<-subset(anchieta_i,!duplicated(anchieta_i[,3]))
anchieta_i[,4]<-NULL
anchieta_i$site<-with(anchieta_i,"anchieta")

fragmentMG<-subset(data, data$Study.reference == "Fadini  R F 2004")
fragmentMG_i<-fragmentMG[,c("Frugivore_Species", "Plant_Species", "interaction")]
fragmentMG_i[,4]<-NULL
fragmentMG_i$site<-with(fragmentMG_i,"fragmentMG")

araucaria<-subset(data, data$Study.reference == "Kindel 1996")
araucaria_i<-araucaria[,c("Frugivore_Species", "Plant_Species", "interaction")]
araucaria_i[,4]<-NULL
araucaria_i$site<-with(araucaria_i,"araucaria")

itatiba<-subset(data, data$Study_Location == "Itatiba, SP")
itatiba_i<-itatiba[,c("Frugivore_Species", "Plant_Species", "interaction")]
itatiba_i[,4]<-NULL
itatiba_i$site<-with(itatiba_i,"itatiba")

fragmentRC<-subset(data, data$Study_Location == "Usina Parque do Corumbatai, Rio Claro - SP")
fragmentRC_i<-fragmentRC[,c("Frugivore_Species", "Plant_Species", "interaction")]
fragmentRC_i[,4]<-NULL
fragmentRC_i$site<-with(fragmentRC_i,"fragmentRC")

restored57<-subset(data, data$Study.reference == "Ribeiro  F (unpublish) 57")
restored57_i<-restored57[,c("Frugivore_Species", "Plant_Species", "interaction")]
restored57_i[,4]<-NULL
restored57_i$site<-with(restored57_i,"restored57")

restored25<-subset(data, data$Study.reference == "Ribeiro  F (unpublish) 25")
restored25_i<-restored25[,c("Frugivore_Species", "Plant_Species", "interaction")]
restored25_i[,4]<-NULL
restored25_i$site<-with(restored25_i,"restored25")

restored15<-subset(data, data$Study.reference == "Ribeiro  F (unpublish) 15")
restored15_i<-restored15[,c("Frugivore_Species", "Plant_Species", "interaction")]
restored15_i[,4]<-NULL
restored15_i$site<-with(restored15_i,"restored15")

comboios<-subset(data, data$Study.reference == "Argel de Oliveira  1999 ")  # note the space after 1999 in the Atlantic 
comboios_i<-comboios[,c("Frugivore_Species", "Plant_Species", "interaction")]
comboios_i[,4]<-NULL
comboios_i$site<-with(comboios_i,"comboios")

itapua<-subset(data, data$Study.reference == "Scherer et al 2007") ### restinga?
itapua_i<-itapua[,c("Frugivore_Species", "Plant_Species", "interaction")]
itapua_i[,4]<-NULL
itapua_i$site<-with(itapua_i,"itapua")

reservasRJ<-subset(data, data$Study_Location == "PARNA Serra Orgaos"|data$Study_Location == "PE Tres Picos, RJ")
reservasRJ_i<-reservasRJ[,c("Frugivore_Species", "Plant_Species", "interaction")]
reservasRJ_i<-subset(reservasRJ_i,!duplicated(reservasRJ_i[,3]))
reservasRJ_i[,4]<-NULL
reservasRJ_i$site<-with(reservasRJ_i,"reservasRJ")


ibitipoca<-subset(data, data$Study.reference == "Manhaes 2003") 
ibitipoca_i<-ibitipoca[,c("Frugivore_Species", "Plant_Species", "interaction")]
ibitipoca_i<-subset(ibitipoca_i,!duplicated(ibitipoca_i[,3]))
ibitipoca_i[,4]<-NULL
ibitipoca_i$site<-with(ibitipoca_i,"ibitipoca")

jurubatiba<-subset(data, data$Study_Location == "Jurubatiba") 
jurubatiba_i<-jurubatiba[,c("Frugivore_Species", "Plant_Species", "interaction")]
jurubatiba_i[,4]<-NULL
jurubatiba_i$site<-with(jurubatiba_i,"jurubatiba")

cardoso_i<-cardoso
cardoso_i<-subset(cardoso_i,!duplicated(cardoso_i[,3]))
cardoso_i[,4]<-NULL
cardoso_i$site<-with(cardoso_i,"cardoso")

botelho_i<-botelho
botelho_i<-subset(botelho_i,!duplicated(botelho_i[,3]))
botelho_i[,4]<-NULL
botelho_i$site<-with(botelho_i,"botelho")

int_list<-list (intervales_i, cardoso_i,botelho_i,
                      rebioAntas_i, anchieta_i, araucaria_i,
                      fragmentMG_i, fragmentRC_i, fragmentSP_i,
                      stagenebra_i, itatiba_i, itapua_i,
                      restored57_i, restored25_i, restored15_i,
                      pira_i, jurubatiba_i, ibitipoca_i,
                      ufrj_i, reservasRJ_i, comboios_i)


int_commu<-merge_all(int_list) # function from reshape
str(int_commu)


############### ------------------- interactions per site
#dt1 <- data.table(itapua_i, key = "interaction") 
#dt2 <- data.table(int_ed_site, key = "interaction")
#t <- left_join (dt1,dt2)
#t1<-subset(t, !duplicated(t[,"interaction"]))

#rm(list=ls())
#save.image("ms_phylogenies.RData")
```


ED and traits (seed diameter and body mass) are correlated for the communities of the Atlantic (ie, native species and interactions with mutualistic seed disperser birds)
```{r ED and traits COMMUNITIES, include=FALSE}

##################working with bird species for the selected communities
#### ------------------- BIRDS - 186 sp among the selected communities - 222 regional level

bm_ED_commu<-join(bm_commu, ED100, by="Frugivore_Species2") # join to get traits and ED same object
bm_unique_commu<-subset(bm_ED_commu,!duplicated(bm_ED_commu[,1])) # using unique spp for the traits correlations
row.names(bm_unique_commu)<-bm_unique_commu$Frugivore_Species2
#bm_unique_commu2<-join(bm_unique_commu, ED100, by = "Frugivore_Species2", type = "left")
bm_unique_commu<-subset(bm_unique_commu[,1:9]) # remove 100 trees


####
##-------------------------PLANTS - 360 spp among the selected communities
#names(ED100_p)[names(ED100_p) == 'Plant_Species'] <- 'Plant_Species'

sd_ED_commu<-join(sd_commu, sd_unique_atl, by="Plant_Species2") 
sd_ED_commu<-sd_ED_commu[,-(9:14)]
sd_unique_commu<-subset(sd_ED_commu,!duplicated(sd_ED_commu[,1])) # using unique spp for the traits correlations
#row.names(sd_unique_commu)<-sd_unique_commu$Plant_Species


```


```{r correlations ED and traits}

#######------------------------------- Correlations
### ----------------Birds
source("~/Dropbox/Phylogenetic interactions/Phylogenies - Metanetwork Miguel/R codes/functions/corPerm.R")


### ----------- regional level
#results_ed_bm<-corPerm3(log(bm_unique_atl$Frug_Body_Mass),bm_unique_atl$mean_birds_ed,nperm=999, tail=2)
#results_ed_bm

### ----------- studies species in the local communities level
results_ed_bm_commu<-corPerm3(log(bm_unique_commu$Frug_Body_Mass),bm_unique_commu$mean_birds_ed,nperm=999, tail=2)
results_ed_bm_commu


par(mfrow=c(1,2))

plot(log(bm_unique_commu$Frug_Body_Mass)~log(bm_unique_commu$mean_birds_ed),
     cex.main=.7,cex.lab=.8, main = "a) Bird Frugivore Species",
     ylab="Body mass (g)",
     xlab="Evolutionary Distinctiveness (log[mean ED])"
     )
    #dev.copy2pdf(file="Figures/ED_bodymass_commu.pdf")

###------------------- Plants

##### ----- regional level - Atlantic
#seed_diam<-as.numeric(sd_unique_atl$seed_diameter) ## 444 species
#results_ed_sd<-corPerm3(log(seed_diam),log(ED100_p$mean_plants_ed),nperm=999, tail=2)
#results_ed_sd

##### ----- community level  ### 360 species
seed_diam1<-as.numeric(sd_unique_commu$seed_diameter)
results_ed_sd_commu<-corPerm3(log(seed_diam1),log(sd_unique_commu$mean_plants_ed),nperm=999, tail=2)
results_ed_sd_commu

plot(log(seed_diam1)~log(sd_unique_commu$mean_plants_ed),
     cex.main=.7,cex.lab=.8, main = "b) Bird-dispersed Plant Species",
     ylab="Seed diameter (mm)",
     xlab="Evolutionary Distinctiveness (log[mean ED])"
     )
    #dev.copy2pdf(file="Figures/ED_sd_commu.pdf")

```


creating a Defaunation index per community
```{r defaunation index, cache = FALSE}

#### loop to calculate the sum of body mass per site
#sum_bm<-NULL
#sites<-as.factor(unique(communities_bm$site))
#sum_body1=NULL
#for (i in sites){
  #commu=subset(communities_bm,site==i)
  #j=sum(commu$Frug_Body_Mass, na.rm=T)
  #result=cbind(i,j)
  #sum_body1=rbind(sum_body1,result)
  #print(i)
  #}

### alternative for the loop
#library(plyr)
sum_bm<-NULL
sum_bm_site=ddply(bm_commu, .(site), summarize, sum_bm=sum(Frug_Body_Mass, na.rm=T))
sum_bm_site

mean_bm<-NULL
mean_bm_site=ddply(bm_commu, .(site), summarize, mean_bm=mean(Frug_Body_Mass, na.rm=T))
mean_bm_site


### regional pool of bodymass
sum_pool<-sum(bm_unique_atl$Frug_Body_Mass, na.rm=T)
mean_pool<-mean(bm_unique_atl$Frug_Body_Mass, na.rm=T)

#### ------------- defaunation index based on body mass
mean_bm_site[,3]<-NULL
mean_bm_site$def_mean<-(1-(mean_bm_site$mean_bm)/mean_pool)
mean_bm_site[,4]<-NULL
mean_bm_site$def_sum<-(1-(sum_bm_site$sum_bm)/sum_pool)

communities1<-with(communities, communities[order(site) , ])
mean_bm_site<-with(mean_bm_site, mean_bm_site[order(site) , ])
new_commu<-cbind(communities1, mean_bm_site)### to merge site data and Defaunation index
def_site<-merge(communities1,mean_bm_site, by= "site", all=T)

#def_site<-cbind.data.frame((new_commu3$site),new_commu3$def_mean,new_commu3$def_sum, new_commu3$area_ha) ### to get only the variables of interest



```


```{r defaunation area correlation}

cor(def_site$def_sum,log(def_site$area_ha)) ### area and defaunation are correlated by -0.63
###### we use the residual of the correlation as the indpendent variable
m1<-lm(def_site$def_sum~log(def_site$area_ha))
summary(m1)

def_resid<-residuals(m1)
def_site[,5]<-NULL
def_site$def_residuals<-def_resid

#### result 
m1b<-lm(def_site$def_sum~(def_site$def_residuals))
summary(m1b)


##plots - add the number of each within the circles
plot(def_site$def_sum~log(def_site$area_ha),
     xlab = "Area of the fragments (log[ha])",
     ylab = "Defaunation index",
     cex.lab=1.3, pch = 19, col = "darkgreen", cex = 2
     )
abline(m1)
#dev.copy2pdf(file="Figures/Def_area.pdf")


```



More defaunated fragments hold interactions performed by less evolutionary distinctive bird and plant species (ED)
testing ED per fragment - area and defaunation
```{r ED of interactions}

#### order dataframes by interaction - 3565 levels of interactions, but 3229 observations

#### calculating the mean ED per interactions

int_commu1<-join(int_commu,sd_unique_commu, by = "Plant_Species", type = "left", match = "first")

int_commu2<-join(int_commu1,bm_unique_commu, by = "Frugivore_Species", type = "left", match = "first")
#int_commu2<-int_commu2[,-(9:14)]
#int_commu2<-int_commu2[,-(10:15)]
int_commu2[,18]<-NULL
int_commu2$int_ed<-with(int_commu2, mean_birds_ed+mean_plants_ed)
int_commu2<-int_commu2[,-(5)]
int_commu2<-int_commu2[,-(6)]
int_commu2<-int_commu2[,-(8:13)]
int_commu2<-int_commu2[,-(9)]

####### calculating mean of interactions ED per site
mean_ED_site<-NULL
mean_int_ED_site=ddply(int_commu2, .(site), summarize, mean_ED_site=mean(int_ed, na.rm=TRUE))
mean_int_ED_site

sum_ED_site<-NULL
sum_int_ED_site=ddply(int_commu2, .(site), summarize, sum_ED_site=sum(int_ed, na.rm=T))
sum_int_ED_site

int_ed_site<-cbind(mean_int_ED_site, sum_int_ED_site)
int_ed_def_site<-cbind(int_ed_site, def_site)
int_ed_def_site <- int_ed_def_site[,-(3),drop=TRUE]
int_ed_def_site <- int_ed_def_site[,-(4),drop=T]
colnames(int_ed_def_site)[colnames(int_ed_def_site) == 'new_commu3$def_mean'] <- 'def_mean'
colnames(int_ed_def_site)[colnames(int_ed_def_site) == 'new_commu3$def_sum'] <- 'def_sum'
colnames(int_ed_def_site)[colnames(int_ed_def_site) == 'new_commu3$area_ha'] <- 'area_ha'
#ed_commu<- int_ed_site1[,-(7:10),drop=T]

par(mfrow=c(1,1))
plot(log(int_ed_def_site$sum_ED_site)~int_ed_def_site$def_sum,
     xlab = "Defaunation",
     ylab = "Sum of Evolutionary Distinctiveness of Interactions")

plot(log(int_ed_def_site$sum_ED_site)~int_ed_def_site$sum_ED_site,
     xlab = "Sum of EDi",
     ylab = "Mean of EDi")
cor(int_ed_def_site$sum_ED_site,int_ed_def_site$mean_ED_site)

plot(log(int_ed_def_site$sum_ED_site)~log(int_ed_def_site$area_ha),
          xlab = "Area of the fragment (log[ha])", xlim = c(12,0),
     ylab = "Sum of Evolutionary Distinctiveness of Interactions")

plot(log(int_ed_def_site$sum_ED_site)~log(int_ed_def_site$area_ha),
          xlab = "Area of the fragment (log[ha])", xlim = c(12,0),
     ylab = "Sum of Evolutionary Distinctiveness of Interactions")
  
#dev.copy2pdf(file="Figures/ED_def_area.pdf")    

### simple linear models
m1<-lm(mean_ED_site~def_sum, data = int_ed_def_site)
summary(m1) #### mean ED per site not related to mean DEF

m2<-lm(sum_ED_site~def_mean, data = int_ed_def_site)
summary(m2) # sum ED per site marginally related to mean DEF

m3<-lm(sum_ED_site~def_sum, data = int_ed_def_site)
summary.lm(m3) ### sums of ED is effected by the Def (sum)

###### selected model used in the MS
final_model<-lm(log(int_ed_def_site$sum_ED_site)~int_ed_def_site$def_residuals)
summary(final_model)

```

```{r mean of ED for EDi}
### in replying to reviewer 1, using the mean of bird and plant ED to create EDi, instead of the sum
int_commu2[,11]<-NULL
int_commu2$int_ed_mean<-with(int_commu2, (mean_birds_ed+mean_plants_ed)/2)

plot(int_commu2$int_ed_mean, int_commu2$int_ed)
cor(int_commu2$int_ed_mean,int_commu2$int_ed)


```



```{r null models for cumulative EDi, Fig R1}
###### NULL MODELS to control for differences in network size affecting cumulative EDi
### transform dataframe into a matrix for the null models 
df_new<-int_commu2[,c("site","interaction", "int_ed")]
matrix_int_ed<-xtabs(int_ed~site+interaction, data=df_new,
                     drop.unused.levels = TRUE) 

#m<-matrix_int_ed[,colSums(matrix_int_ed^2) !=0] # drop columns with only zeros


##### null models to test whether the observed ED per fragment is higher/lower than expected by chance, considering the size of the matrix, ie. number of species in each community
nulls_int<-bipartite::nullmodel(matrix_int_ed,method=4, N=100)
nulls2i<-lapply(nulls_int, FUN = rowMeans, na.rm=TRUE)
nulls3i<- sapply(nulls2i,function(x) sapply(x, function(x) mean(x,na.rm=TRUE)) )
mean_nulls_ed_int<-rowMeans(nulls3i)
sd_nulls_ed_int<-apply(nulls3i, 1, sd)

ses.ed_int<-(rowMeans(matrix_int_ed)-mean_nulls_ed_int)/sd_nulls_ed_int


###### include these results in the SM
results_ses_ed_int<-lm(ses.ed_int~(int_ed_def_site$def_sum))
summary.lm(results_ses_ed_int)
par(mfrow=c(1,1))
plot((ses.ed_int)~(int_ed_def_site$def_sum), 
     main="t= -4.811, p< 0.001",cex.main=.8,
     ylab="Deviation from null models (EDi[MY])",cex.lab=0.9,
     ylim = c(-20,70),
     xlab="Intensity of defaunation",
     pch = 19, col = "light blue", cex = 2
     )
text((int_ed_def_site$ses.ed_int), int_ed_def_site$def_sum, int_ed_def_site$ID_new) 
int_ed_def_site<-cbind(ses.ed_int,int_ed_def_site)
ls(int_ed_def_site)
abline(results_ses_ed_int)
dev.copy2pdf(file="Figures/EDint_def_nullmodels.pdf")


############# ggplot
p<-ggplot(int_ed_site2, aes(x= def_sum, y= (ses.ed_int1), colour="green", label=ID_new)) +
  geom_text(aes(label=ID_new),hjust=.6, vjust=0.5, color = "black", size = 4)
p + geom_point(color = "blue", size = 8, shape = 21, stroke = .5) +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) +
  theme(axis.title.x = element_text(size=12),
      axis.title.y = element_text(size=12)) +
   labs(y="Deviation from null models (EDi[MY])", x = "Intensity of defaunation")


### removing intervales
#int_ed_site2<-int_ed_def_site[-10,]
#ses.ed_int1<-ses.ed_int[-10]
#results_ses_ed_int1<-lm(ses.ed_int1~(int_ed_site2$def_sum))
#summary.lm(results_ses_ed_int1)


#plot(ses.ed_int1~(int_ed_site2$def_sum), 
 #    main="t= -4.917, p< 0.001",cex.main=.8,
  #   ylab="Deviation from null models (ED[MY])",cex.lab=0.9,
   #  xlab="Defaunation index"
    # )
#abline(results_ses_ed_int1)
#dev.copy2pdf(file="Figures/EDint_def_nullmodels_RemovedIntervales.pdf")


#######

save.image("ms_phylogenies2.RData")
```

```{r resample Intervales}
### the idea is to resample intervales according to the N of interactions observed in the smaller area fragment (26), then compare the total EDi
# differences in total EDi indicates the loss is not at random
## think on a null model for this

df1<-as.data.frame(intervales_i$interaction)
colnames(df1)[1]<-"interaction"
df2<-join(df1,int_commu2, by = "interaction", type = "left", match = "first")

#### code to sample Intervales 26 times, and obtain the sum EDi per sample

df<-select(df2, interaction, int_ed)
output <- lapply(1:1000, function(rep) {
    sample_n((df), 26, replace = FALSE) %>%
    summarize(sum_x = sum(int_ed)) %>%
    mutate(replicate=rep)
})
rep_df <- do.call(rbind, output)
(rep_df)

mean_sub_intervales<-mean(as.numeric(rep_df$sum_x), na.rm = TRUE)
sd_sub_intervales<-sd(as.numeric(rep_df$sum_x), na.rm = TRUE)
z_sub_intervales<-(sum_int_ED_site[21,2]-mean_sub_intervales)/sd_sub_intervales
z_sub_intervales#### there is no difference from the observed EDi of the smaller area and the sub-sampled Intervales --- DOES IT MAKE SENSE?

#### code to sample Intervales 26 times, and obtain the sum EDi per sample

df3<-select(df2, interaction, Frug_Body_Mass)
output <- lapply(1:1000, function(rep) {
    sample_n((df3), 26, replace = FALSE) %>%
    summarize(sum_x = sum(Frug_Body_Mass)) %>%
    mutate(replicate=rep)
})
rep_df3 <- do.call(rbind, output)
(rep_df3)

mean_sub_intervales3<-mean(as.numeric(rep_df3$sum_x), na.rm = TRUE)
sd_sub_intervales3<-sd(as.numeric(rep_df3$sum_x), na.rm = TRUE)
z_sub_intervales3<-(sum_bm_site[21,2]-mean_sub_intervales3)/sd_sub_intervales3
z_sub_intervales3#### there is no difference from the observed EDi of the smaller area and the sub-sampled Intervales --- DOES IT MAKE SENSE?




#####
#HISTOGRAMS FOR BODYMASS OF INTERVALES AND UFRJ
par(mfrow=c(4,4))
hist((bm_commu[bm_commu$site=="intervales",]$Frug_Body_Mass),xlab="Birds body mass (g)", main= "1", col="lightgreen")
hist((bm_commu[bm_commu$site=="botelho",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "2", col="lightgreen")
hist((bm_commu[bm_commu$site=="reservasRJ",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "3", col="lightgreen")
hist((bm_commu[bm_commu$site=="jurubatiba",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "4", col="lightgreen")
hist((bm_commu[bm_commu$site=="cardoso",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "5", col="lightgreen")
hist((bm_commu[bm_commu$site=="itapua",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "6", col="lightgreen")
hist((bm_commu[bm_commu$site=="rebioAntas",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "7", col="lightgreen")
hist((bm_commu[bm_commu$site=="ibitipoca",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "8", col="lightgreen")
hist((bm_commu[bm_commu$site=="comboios",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "9", col="lightgreen")
hist((bm_commu[bm_commu$site=="anchieta",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "10", col="lightgreen")
hist((bm_commu[bm_commu$site=="fragmentMG",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "11", col="lightgreen")
hist((bm_commu[bm_commu$site=="araucaria",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "12", col="lightgreen")
hist((bm_commu[bm_commu$site=="stagenebra",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "13", col="lightgreen")
hist((bm_commu[bm_commu$site=="itatiba",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "14", col="lightgreen")
hist((bm_commu[bm_commu$site=="fragmentRC",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "15", col="lightgreen")
hist((bm_commu[bm_commu$site=="restored57",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "16", col="lightgreen")
hist((bm_commu[bm_commu$site=="restored15",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "17", col="lightgreen")
hist((bm_commu[bm_commu$site=="restored25",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "18", col="lightgreen")
hist((bm_commu[bm_commu$site=="fragmentSP",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "19", col="lightgreen")
hist((bm_commu[bm_commu$site=="pira",]$Frug_Body_Mass), xlab="Birds body mass (g)", main= "20", col="lightgreen")
hist((bm_commu[bm_commu$site=="ufrj",]$Frug_Body_Mass),xlab="Birds body mass (g)", main= "21", col="lightgreen") 

```


ED and centrality (k, number of fragments in which the interaction occurs)
```{r degree of interactions}
### transform dataframe into a matrix for centrality

matrix_bin<-matrix_int_ed
matrix_bin[matrix_bin > 0] = 1
write.csv(matrix_bin, "nested_interactions1.csv")

###### matrix occurrence of birds
occ_birds<-xtabs(int_ed~Frugivore_Species+site, data=int_commu2)
dim(occ_birds)
occ_birds[occ_birds > 0] = 1

###### matrix occurrence of plants
occ_plants<-xtabs(int_ed~Plant_Species+site, data=int_commu2)
dim(occ_plants)
occ_plants[occ_plants > 0] = 1

###### matrix nestedness of birds
nested_birds<-xtabs(mean_birds_ed~site+Frugivore_Species, data=bm_commu)
dim(nested_birds)
nested_birds[nested_birds > 0] = 1

###### matrix nestedness of plants
nested_plants<-xtabs(mean_plants_ed~site+Plant_Species, data=sd_ED_commu)
dim(nested_plants)
nested_plants[nested_plants > 0] = 1


##### calculating degree of interactions
k_int<-specieslevel (matrix_bin, level = "higher", index = "degree")
k_int<-rownames_to_column(k_int, var="interaction") ## transform rownmaes to columns #library(tibble)

setdiff(k_int$interaction,int_commu2$interaction)
setdiff(int_commu2$interaction,k_int$interaction)

ed<-join(k_int,int_commu2,by = "interaction", type = "left", match = "first")


##### calculating degree of bird species
k_birds<-specieslevel (nested_birds, level = "higher", index = "degree")
k_birds<-rownames_to_column(k_birds, var="Frugivore_Species") 
traits_birds<-join(bm_ED_commu,k_birds,by = "Frugivore_Species", match= "first", type = "left")
#write.csv(traits_birds, "birds_traits.csv")

##### calculating degree of plant species
k_plants<-specieslevel (nested_plants, level = "higher", index = "degree")
k_plants<-rownames_to_column(k_plants, var="Plant_Species") 
traits_plants<-join(sd_ED_commu,k_plants,by = "Plant_Species", match= "first", type = "left")
#write.csv(traits_plants, "plants_traits.csv")


####### mean of bird and plants as additive response variables to test the effec to defaunation in the interaction centrality
####### scale of the means - similar results, nothing significant when using means
ed$mean_birds_ed_scl<-ed$mean_birds_ed/max(ed$mean_birds_ed, na.rm = TRUE)
ed$mean_plants_ed_scl<-ed$mean_plants_ed/max(ed$mean_plants_ed,na.rm = TRUE)
ed["mean_birds_ed_scl"]<-ed$mean_birds_ed/max(ed$mean_birds_ed, na.rm = TRUE)
ed["mean_plants_ed_scl"]<-ed$mean_plants_ed/max(ed$mean_plants_ed,na.rm = TRUE)


mk<-glmer(degree~(mean_birds_ed_scl)+(mean_plants_ed_scl) +
            (1|Frugivore_Species)+(1|Plant_Species),data=ed,family="poisson")
summary(mk) ## only birds are significant

mk1<-glmer(degree~(mean_birds_ed_scl)+ (1|Frugivore_Species),data=ed,family="poisson") ## simplified model
summary(mk1) ## only birds are significant 

par(mfrow=c(1,2))
plot(degree~(mean_birds_ed), data=ed, 
     #main="t= -2.074, p=0.0381, glmer",
     cex.main=.7,
     ylab="N fragments in which the interaction occurs",cex.lab=0.8,
     xlab="Evolutionary Distinctness of bird species (MY)"
     )

plot(degree~(mean_plants_ed), data=ed, 
     cex.main=.7,
     ylab="N fragments in which the interaction occurs",cex.lab=0.8,
     xlab="Evolutionary Distinctness of plant species (MY)"
     )

dev.copy2pdf(file="Fig. k_int vs ED.pdf")

######MCMC -  change results each time it is run! more stable with higher nitt and burnin
#library(MCMCglmm)
#ed$family<-NULL
#rmcmc_k<-MCMCglmm(degree~log(mean_birds_ed)+log(mean_plants_ed),
 #                 random=~Frugivore_Species+Plant_Species,family="poisson",data=ed, 
  #                nitt=1000000, burnin = 10000)
#summary(rmcmc_k)
#plot(rmcmc_k)

#rmcmc_bc<-MCMCglmm(log(bc_int+1)~log(mean_birds_ed)+log(mean_plants_ed),
 #                 random=~birds+plants,data=ed)
#summary(rmcmc_bc)


```


Asymmetries 
```{r asymmetries}
#ed<-int_commu2
ed_unique<-subset(ed,!duplicated(ed[,1])) #### testing with unique interactions

##### testing whether interactions are symmetric
#asym_test<-corPerm3(ed1$mean_birds_ed,ed1$mean_plants_ed, nperm = 999, tail = 2)
#asym_test

#asym_scl_test<-corPerm3(ed1$mean_birds_ed_scl,ed1$mean_plants_ed_scl, nperm = 999, tail = 2)
#asym_scl_test

### dij= (Ai-Bj)/max(Ai,Bj)
#A= mean_birds_ed
#B= mean_plants_ed
## + values - more ED birds w less ED plants
## - values - less ED birds w more ED plants


####### testing with total interactions - 3230
#asym<-NULL
#for (i in 1:nrow(ed)){
 #asym [i]<- (ed$mean_birds_ed[i]-ed$mean_plants_ed[i])/max(ed$mean_birds_ed[i],ed$mean_plants_ed[i])
#}
#ed["asym"]<-asym
#ed$asym


#asym_scl<-NULL
#for (i in 1:nrow(ed)){
 #asym_scl [i]<- (ed$mean_birds_ed_scl[i]-ed$mean_plants_ed_scl[i])/max(ed$mean_birds_ed_scl[i],ed$mean_plants_ed_scl[i])
}
#ed["asym_scl"]<-asym_scl


#### testing whether ED asymmetry values are different than zero, therefore asymmetric
#t.test(ed$asym)




######## testing with unique interactions 2669
### use scaled asymmetries only

asym_scl<-NULL
for (i in 1:nrow(ed_unique)){
 asym_scl [i]<- (ed_unique$mean_birds_ed_scl[i]-ed_unique$mean_plants_ed_scl[i])/max(ed_unique$mean_birds_ed_scl[i],ed_unique$mean_plants_ed_scl[i])
}
ed_unique["asym_scl"]<-asym_scl
hist(ed_unique$asym_scl)

t.test(ed_unique$asym_scl)



#### scaled
type_scl<-NULL
type_asym_scl<-ifelse(ed_unique$asym_scl > 0,"positive","negative")
ed_unique["type_asym_scl"]<-type_asym_scl
#write.csv(ed, "ed_traits_new.csv")



########## Asymmetries and degree to test whether more asymetric interactions are related to more persisting interactions



plot(ed1$degree~ed1$asym,xlab="ED of interaction asymmetry",
    ylab="N fragments in which the interaction occurs")
     #main = "z= -2.239, p = 0.025")
plot(ed$asym~ed$degree,ylab="Interaction asymmetry of ED",
     xlab="N fragments in which the interaction occurs")
     #main = "z= -2.239, p = 0.025")
dev.copy2pdf(file="Fig. k_int vs asymmetry.pdf")


########## Testig whether more asymetric interactions are related to more persisting birds and plants
mk4<-glmer(degree~mean_birds_ed_scl + mean_plants_ed_scl + (1|Frugivore_Species),data=ed_unique,family="poisson")
summary(mk4)

mk5<-glmer(degree~mean_plants_ed_scl + (1|Plant_Species),data=ed_unique,family="poisson")
summary(mk5)

#####
#CONTOUR PLOTS OPTION
library(plotly)
  x = (ed_unique$mean_plants_ed_scl)
  y = (ed_unique$mean_birds_ed_scl)

####
cols<-c("blue", "yellow")
q<-ggplot(data=ed_unique, aes(x=x, y=y, z=asym_scl)) +
stat_density2d(aes(alpha=..level..), contour=TRUE, geom="polygon", colour= "blue") +
geom_density2d(size=1)+
  scale_y_continuous(limits = c(0,.5)) +
  scale_x_continuous(limits = c(0,.5)) +
  labs(y="Birds Evolutionary Distinctiveness (log)", x = "Plants Evolutionary Distinctiveness (log)") +
  geom_point(aes(colour = asym_scl), shape = 21, size = 1, stroke = 0.2)+
  scale_colour_gradient(low="dark green", high="orange") +
             
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) +
 geom_abline(intercept = 0, slope = 1, colour='gray', linetype=2) +
theme(axis.title.x = element_text(size=14),
      axis.title.y = element_text(size=14))
q
# add marginal histograms
#library(ggExtra)
#ggExtra::ggMarginal(q, type = "histogram")

dev.copy2pdf(file="Fig. asymmetries new.pdf")
save.image("ms_phylogenies2.RData")

```

Figures
```{r figure science,eval=FALSE}

bt100<-read.newick("birds_solved100_trees.nwk")

#Three plots to compose a nice figure for your Science paper
dev.off()
#ed["mean_birds_ed"] <- rowMeans(ed[,2:101])
ed_birds<-subset(ed,!duplicated(ed[,2]))
#ed_birds_unique<-subset(ed,!duplicated(ed[,1]))
traits1<-subset(ed_birds, select = c("Frugivore_Species2","Frug_Body_Mass","mean_birds_ed"))
                                        #    "k_birds", 
dim(traits1)
#traits1$birds <- sub(" ", "_", traits1$birds)
#write.csv(traits1,"birds_unique.csv")

rownames(traits1)<-traits1$Frugivore_Species2
traits1$birds<-NULL



########## code by Miguel
####
tree<- bt100[[1]]#read tree birds
sp_remove<-setdiff(tree$tip.label,traits1$Frugivore_Species2) ## select species from the regional pool not recorded in the studied communities
tree1<-drop.tip(tree, sp_remove) ## remove species from the regional pool tree

traits1<-traits1[tree1$tip.label,]
colorstraits<-colorRampPalette(colors=c("white","black"))(2)
phylo.heatmap(tree,traits1, colors=colorstraits, fsize=0.2)
#dev.copy2pdf(file="Figures/Heatmap_traits_nat.pdf")


###### occurrence

###### matrix occurrence of birds
occ_birds<-xtabs(int_ed~Frugivore_Species2+site, data=int_commu2)
dim(occ_birds)
occ_birds[occ_birds > 0] = 1

occurrence<-occ_birds[tree1$tip.label,]
colorstraits<-colorRampPalette(colors=c("white","black"))(100)
phylo.heatmap(tree,occ_birds,fsize=1, labels=TRUE)
#dev.copy2pdf(file="Figures/Heatmap_sp_occurrence_birds.pdf")
#dev.copy2pdf(file="Figures/Fig_occurrence_birds.pdf")


#### mapping evolutionary history in the tree
birds_ed2<-traits1$mean_birds_ed
names(birds_ed2)<-rownames(traits1)

obj<-contMap(tree1,birds_ed2,plot=FALSE, fsize=0.05, lwd = .5, type = "fan")
n<-length(obj$cols)
obj$cols[1:n]<-colorRampPalette(c("blue","yellow"), space="Lab")(n)
plot(obj, type="fan", fsize=.8, lwd=3)
dev.copy2pdf(file="Figures/Heatmap_ED_birds_fan.pdf")

save.image("ms_phylogenies1.RData")
#rm(list=ls())

#----------------------------------------------------------------------------plants
############
#### plants
tt100<-read.newick("plants_100trees.nwk")

#Three plots to compose a nice figure for your Science paper
dev.off()

ed_plants<-subset(ed,!duplicated(ed[,3]))
traits1p<-subset(ed_plants, select = c("Plant_Species","seed_diameter","mean_plants_ed"))
                                        #    "k_birds", 
traits1p$Plant_Species2 <- sub(" ", "_", traits1p$Plant_Species)
rownames(traits1p)<-traits1p$Plant_Species2
traits1p$plants<-NULL

########## code by Miguel
####
treep<- tt100[[1]]
plants_remove<-setdiff(treep$tip.label,traits1p$Plant_Species2)
tree1p<-drop.tip(treep, plants_remove) 

traits1p<-traits1p[tree1p$tip.label,]
colorstraits<-colorRampPalette(colors=c("white","black"))(2)
#phylo.heatmap(tree,traits1, colors=colorstraits, fsize=0.2)
#dev.copy2pdf(file="Figures/Heatmap_traits_nat.pdf")

#phylo.heatmap(treep,traitsp, colors=colorstraits, fsize=0.2)
#dev.copy2pdf(file="Figures/Heatmap_traits_plants.pdf")
#setdiff(rownames(traits1p),tree1p$tip.label)
#which(rownames(traitsp)=="Rhipsalis_campos portoana")
#rownames(traitsp)[[54]]<-"Rhipsalis_campos_portoana"

#dev.new()
#setdiff(rownames(occurrence_plants),treep$tip.label)

###### matrix occurrence of plants
occ_plants<-xtabs(int_ed~Plant_Species+site, data=int_commu2)
dim(occ_plants)
occ_plants[occ_plants > 0] = 1

occurrence_plants<-occ_plants[tree1p$tip.label,]
#oc_binary<-ifelse(occurrence_plants>0,1,0)
colorstraits<-colorRampPalette(colors=c("white","black"))(2)
phylo.heatmap(treep,occurrence_plants,fsize=1, legend=TRUE)## check if labels=FALSE works
#dev.copy2pdf(file="Figures/Heatmap_plants_occurrence.pdf")
#dev.copy2pdf(file="Figures/Fig_plants_occurrence.pdf")

#### mapping evolutionary history in the tree
plants_ed2<-traits1p$mean_plants_ed
names(plants_ed2)<-rownames(traits1p)

obj<-contMap(tree1p,plants_ed2,plot=FALSE, fsize=0.05, lwd = .5, type = "fan")
n<-length(obj$cols)
obj$cols[1:n]<-colorRampPalette(c("blue","yellow"), space="Lab")(n)
plot(obj, type="fan", fsize=.8, lwd=3)
dev.copy2pdf(file="Figures/Heatmap_ED_plants_fan.pdf")


save.image("ms_phylogenies1.RData")

#rm(list=ls())

```


